---
title: "Data 607 Assignment 1"
author: "Melissa Bowman"
date: "September 4, 2022"
output:
  html_document: default
  pdf_document: default
---

In this assignment, dataset and subset are explored. The data chosen was the 2022 FiveThirtyEight Election Forecastdatasets (senate only) on fivethirtyeight.com (link: https://github.com/fivethirtyeight/data/tree/master/election-forecasts-2022)

The first part of the assignment is to read the data through its raw code for reproducibility. Here the data's raw code was extracted from a GitHub repository. In the original dataset a column name called cycle was changed to 2022_cycle and a subset of data was taken from when the mean number of senate seats held by democrats was more than 50. This is the threshold of control over the senate. 

## Load libraries.
```{r libraries}
library(RCurl)
library(dplyr)
```
## Import CSV from Raw File



```{r reading csv file from Github}
df = read.csv('https://projects.fivethirtyeight.com/2022-general-election-forecast-data/senate_national_toplines_2022.csv')
```

## Checking Variables

You can also embed plots, for example:

```{r head of df}
head(df)

```

## Renaming a Column and Showing just Names of Column
```{r}
names(df)[names(df)=="cycle"] <- "2022_cycle"
names(df)
```
## Subsetting Data

Question for Subset Data: What date does the mean of the democratic party exceed 50? Why is this data interesting?

```{r}
df_col_exclude = 
  df %>% select(-branch, -expression, -chamber_Dparty, -chamber_Rparty,
                -p10_seats_Dparty, -p10_seats_Rparty)

D_party_control_senate <- subset(df_col_exclude, mean_seats_Dparty > 50)


head(D_party_control_senate %>% arrange(forecastdate))
```

